Thesis outline

### 2017-07-19 KellyDouglass/Thesis/DirectMethodPhysics.tex
Added acknowledgments and dedication
Fixed typos

\chapter[Direct method physics]{The physics of the Direct $T_e$ method}\label{sec:physics}

@@

A time-dependent potential is added to the Schr\"{o}dinger equation in order to 
solve for the forbidden transition energies.  We can assume that the time 
perturbation is a minor component of the potential and can thus treat it as a 
perturbation.  For a simplified two-level system, the time-dependent wave 
function is
\begin{equation}
    \Psi (t) = c_a (t) \psi_a e^{iE_a t/\hbar} + c_b (t) \psi (b) e^{-iE_b t/\hbar}
\end{equation}
To solve for the time-dependent coefficients, we substitute $\Psi (t)$ into the 
time-dependent Schr\"{o}dinter equation
\begin{equation}
    H\Psi = i\hbar \frac{\partial \Psi}{\partial t}, \qquad \text{where } H = H^0 + H'(t)
\end{equation}
We find that
\begin{align}
    \dot{c}_a &= -\frac{i}{\hbar} H'_{ab} e^{-i\omega_0 t} c_b\\
    \dot{c}_b &= -\frac{i}{\hbar} H'_{ba} e^{-i\omega_0 t} c_a
\end{align}
where
\begin{equation}
    \omega_0 \equiv \frac{E_b - E_a}{\hbar}
\end{equation}
and
\begin{equation}
    H_{ij} \equiv \langle \psi_i | H' | \psi_j \rangle
\end{equation}
The probability that transmission has occurred is $P_{b\to a} = |c_a (t)|^2$.  
The transmission rate $R_{a\to b} = dP/dt$.

>>>>

\chapter[Direct Method Physics]{Physics of the Direct $T_e$ Method}\label{sec:physics}

@@

A time-dependent potential is added to the Schr\"{o}dinger equation in order to 
solve for the forbidden transition energies.  We can assume that this 
time-dependent potential is a minor component of the potential and can thus 
treat it as a perturbation.  For a simplified two-level system, the 
time-dependent wave function is
\begin{equation}
    \Psi (t) = c_a (t) \psi_a e^{iE_a t/\hbar} + c_b (t) \psi (b) e^{-iE_b t/\hbar}
\end{equation}
To solve for the time-dependent coefficients, we substitute $\Psi (t)$ into the 
time-dependent Schr\"{o}dinger equation
\begin{equation}
    H\Psi = i\hbar \frac{\partial \Psi}{\partial t}, \qquad \text{where } H = H^0 + H'(t)
\end{equation}
We find that
\begin{align}
    \dot{c}_a &= -\frac{i}{\hbar} H'_{ab} e^{-i\omega_0 t} c_b\\
    \dot{c}_b &= -\frac{i}{\hbar} H'_{ba} e^{-i\omega_0 t} c_a
\end{align}
where
\begin{equation}
    \omega_0 \equiv \frac{E_b - E_a}{\hbar}
\end{equation}
and
\begin{equation}
    H_{ij} \equiv \langle \psi_i | H' | \psi_j \rangle
\end{equation}
The probability that transmission has occurred is $P_{b\to a} = |c_a (t)|^2$.  
The transmission rate $R_{a\to b} = dP/dt$.

### 2017-07-19 KellyDouglass/Thesis/Tables/Paper1/XMPtable.tex
Fixed typos

\caption[Extremely low-metallicity dwarf galaxies in 135 galaxy sample]{Details of the 21 extreme low gas-phase metallicity ($12 + \log(\text{O}/\text{H}) < 7.6$) galaxies found.  Four of these galaxies are located in voids (about 10\% of the void dwarf population measured) and seventeen are in more dense regions (about 19\% of the wall dwarf population measured); thus, there does not seem to be a special population of extreme low-metallicity galaxies in voids.  Further study of these galaxies is recommended to confirm metallicity values and identify any shared characteristics.}

>>>>

\caption[Extremely low-metallicity dwarf galaxies in 135 dwarf galaxy sample]{Details of the 21 extreme low gas-phase metallicity ($12 + \log(\text{O}/\text{H}) < 7.6$) galaxies found.  Four of these galaxies are located in voids (about 10\% of the void dwarf population measured) and seventeen are in more dense regions (about 19\% of the wall dwarf population measured); thus, there does not seem to be a special population of extreme low-metallicity galaxies in voids.  Further study of these galaxies is recommended to confirm metallicity values and identify any shared characteristics.}

### 2017-07-19 KellyDouglass/Thesis/Thesis_sections/Conclusion.tex
Fixed typos

\chapter[Conclusion]{Conclusions and suggestions for future work}\label{ch:conclusion}

@@

% Shift in O/H
By deriving a relation between the doubly-ionized oxygen and total oxygen 
abundance in star-forming galaxies, we can expand our sample to consist of 1920 
star-forming dwarf galaxies by removing the dependence on the [\ion{O}{2}] 
$\lambda$3727 doublet.  This larger sample exhibits the same shifts in the 
gas-phase chemical abundances as the smaller, 135 star-forming dwarf galaxy 
sample, but with a much higher statistical significance.  We find that 
star-forming void dwarf galaxies have, on average, 7\% higher oxygen abundances 
than star-forming dwarf galaxies in denser regions.  This shift in the gas-phase 
oxygen abundance distribution could be observational evidence for delayed star 
formation in void galaxies when compared to those in denser regions.  This would 
result in a smaller ratio of stellar mass to dark matter halo mass in void 
galaxies than in dwarf galaxies in denser regions, as predicted in simulations 
by \cite{Jung14} and \cite{Tonnesen15}.  If the void galaxies are retaining more 
oxygen as a result of their deeper potential wells (relative to galaxies of the 
same stellar mass in dense regions), then they would be able to commence 
secondary nitrogen synthesis earlier.  We find that some of the star-forming 
dwarf galaxies have a constant value of N/O for a range of masses while the 
remainder exhibit a positive relationship between the stellar mass and N/O ratio 
in the $M_*$-N/O relationship.  We make note of a different critical mass in the 
$M_*$-N/O relationship in the two environments, where the void dwarf galaxies 
begin to show evidence of secondary nitrogen synthesis at a stellar mass 
$\sim$0.4 dex lower than for the galaxies in denser regions.  This indicates 
that the void galaxies synthesize secondary nitrogen at a smaller stellar mass 
than galaxies in denser regions.

@@

It has been hypothesized that a special population of extremely metal-poor 
galaxies exist in void regions.  We find no evidence for a special population of 
extremely metal-poor star-forming dwarf galaxies in the voids, as we note an 
equal fraction of low metallicity dwarf galaxies in both the void and denser 
regions.  Due to their low gas-phase oxygen abundances, these 287 dwarf galaxies 
have some of the larger N/O ratios of the star-forming dwarf galaxies sample 
studied.  While the metallicities of these galaxies cause them to stand out in 
the relationships between metallicity and other physical quantities (stellar 
mass, color, (s)SFR), they are not unusual when studying the relationships 
between the N/O ratio and these other quantities.

% Small-scale environment
\section[Small-scale environment]{Small-scale environmental influence on dwarf galaxy evolution}
In addition to the influence of the large-scale environment on the evolution of 
dwarf galaxies, we also study the effects of the small-scale environment on dwarf 
galaxies.  We find that only the presence of a neighboring galaxy within 0.05 
\hMpc or 0.1$r_{vir}$, or the presence of a group within 0.1 \hMpc influences a 
dwarf galaxy's evolution.  Dwarf galaxies with a nearest neighbor galaxy within 
0.05 \hMpc or 0.1$r_{vir}$ tend to be bluer, have a higher sSFR, and have higher 
oxygen and nitrogen abundances than average.  This matches the results of 
\cite{Park09}, who find that higher luminosity late-late type galaxy pairs 
within 0.05$r_{vir}$ are bluer and have higher SFRs.  In contrast, dwarf 
galaxies within 0.1 \hMpc of the center of the closest group are redder, have 
lower oxygen abundances, and have higher N/O ratios than average.  These results 
are independent of both the maximum relative velocity required to define a 
nearest neighbor and the sample (star-forming versus all dwarf galaxies).

@@

% GV galaxies
\section[GV galaxies]{Properties of green valley galaxies}
Finally, we also investigate the properties of galaxies residing in the green 
valley of the color-magnitude diagram (CMD) in an effort to understand the role 
of the environment on a galaxy's evolution through the color-magnitude diagram.  
We discover that we can define galaxies which are transitioning through the 
green valley of the CMD by combining the galaxy's color, color gradient, and 
inverse concentration index.  Galaxies with a value aimc$< 25$ for the 
morphological type as calculated in the KIAS-VAGC exist in the green valley 
portion of the UV-optical CMD.  Galaxies defined as early types (morphological 
type values equal to 1 or 2) are in the red cloud, while those with 
morphological type values greater than 25 are in the blue sequence.  With this 
quantitative definition for galaxies transitioning through the green valley, we 
can begin to understand the properties of green valley galaxies and their 
evolution.

Based on our analysis, green valley galaxies have stellar masses comparable to 
galaxies in the red cloud.  They have intermediate SFRs and low-to-intermediate 
sSFRs.  Green valley galaxies also have high gas-phase nitrogen abundances 
(N/H), resulting in high N/O ratios.  While their SFRs show that their star 
formation has been quenched, their stellar masses inform us that this is not due 
to any premature quenching mechanism.  The high nitrogen abundances in the green 
valley galaxies indicate that the galaxies are either no longer forming stars 
(since nitrogen is produced in lower mass stars than oxygen), or that the 
galaxies were able to synthesize both primary and secondary nitrogen (heavy 
elements were present during the last few star formation episodes to permit the 
CNO cycle to commence earlier).  This chemical abundance pattern of normal 
oxygen (O/H), high nitrogen (N/H), and high N/O ratio is also seen in galaxies 
classified as AGN, indicating that galaxies in the green valley have an AGN.

The fraction of void galaxies that are found in the green valley is 
significantly smaller than the fraction of green valley galaxies found in denser 
regions.  Combined with the previous results about the large-scale environmental 
influence on the gas-phase chemical abundances, this indicates that void dwarf 
galaxies are less evolved than dwarf galaxies in denser environments.

@@

A critical problem in galaxy formation is understanding how galaxies transition 
from the blue sequence to the red cloud in the optical color-magnitude diagram.  
Star formation is thought to be quenching in galaxies moving through the green 
valley, but the relevant baryonic processes (gas cooling, feedback, etc.) are 
very complex and heavily independent.  The enrichment of the interstellar medium 
(ISM) and circumgalactic medium (CGM) of a galaxy involves many complicated 
processes, the interplay of which is not yet well understood.  Investigating the 
star formation history and chemical evolution of galaxies in the green valley 
should provide clues of the movement of a galaxy through the color-magnitude 
diagram.

With the advent of 2-dimensional spectroscopic data from SDSS MaNGA \citep{MaNGA,
SDSS13}, it is possible to examine how the ISM and CGM are enriched over time.  
MaNGA is the first large-scale survey using integral-field spectroscopy, which 
would permit the study of spatially-resolved physical properties of galaxies 
across many different environments, morphologies, and stages of evolution.  In 
particular, it would be instructive to study the gradients of the gas-phase 
chemical abundances of galaxies in order to better understand their evolution 
through the CMD and also the influence of the environment in both large and 
small scales on the chemical evolution of these galaxies.

@@

A better knowledge of the chemical abundances of galaxies with an AGN is also 
crucial to understanding the evolution of galaxies.  Understanding how the 
presence of an AGN affects a galaxy's evolution is currently limited --- at the 
moment, most research is concentrated on the physics within an AGN.  Many 
simulations have been done to test different theories about the role of an AGN 
in a galaxy, and observations are now needed to test the results of the 
simulations.

@@

The work done here on the small-scale environment is only the beginning of what 
can be done in this subject area.  In addition to studying the relationship 
between a galaxy's physical parameters and its distance to the nearest neighbor, 
it is also important to look at the ratio of the galaxy's parameters to its 
neighbor's and the distance to the nearest neighbor --- ``galactic 
conformity.''  These comparisons should include a morphological comparison, 
similar to the analysis done by \cite{Park09}.  We also find evidence of 
possible mergers when studying the influence of the small-scale environment.  
Visual inspection of these dwarf galaxies is imperative to confirming this 
conclusion.

>>>>

\chapter[Conclusions]{Conclusions and suggestions for future work}\label{ch:conclusion}

@@

% Shift in O/H
By deriving a relation between the doubly-ionized oxygen and total oxygen 
abundance in star-forming galaxies, we can expand our sample to consist of 1920 
star-forming dwarf galaxies by removing the dependence on the [\ion{O}{2}] 
$\lambda$3727 doublet.  This larger sample exhibits the same shifts in the 
gas-phase chemical abundances as the smaller, 135 star-forming dwarf galaxy 
sample but with a much higher statistical significance.  We find that 
star-forming void dwarf galaxies have, on average, 7\% higher oxygen abundances 
than star-forming dwarf galaxies in denser regions.  This shift in the gas-phase 
oxygen abundance distribution could be observational evidence for delayed star 
formation in void galaxies when compared to those in denser regions.  This would 
result in a smaller ratio of stellar mass to dark matter halo mass in void 
galaxies than in dwarf galaxies in denser regions, as predicted in simulations 
by \cite{Jung14} and \cite{Tonnesen15}.  If the void galaxies are retaining more 
oxygen as a result of their deeper potential wells (relative to galaxies of the 
same stellar mass in dense regions), then they would be able to commence 
secondary nitrogen synthesis earlier.  We find that some of the star-forming 
dwarf galaxies have a constant value of N/O for a range of masses while the 
remainder exhibit a positive relationship between the stellar mass and N/O ratio 
in the $M_*$-N/O relationship.  We make note of a different critical mass in the 
$M_*$-N/O relationship in the two environments, where the void dwarf galaxies 
begin to show evidence of secondary nitrogen synthesis at a stellar mass 
$\sim$0.4 dex lower than for dwarf galaxies in denser regions.  This indicates 
that the void dwarf galaxies begin to synthesize secondary nitrogen at a smaller 
stellar mass than dwarf galaxies in denser regions.

@@

It has been hypothesized that a special population of extremely metal-poor 
galaxies exist in void regions.  We find no evidence for a special population of 
extremely metal-poor star-forming dwarf galaxies in the voids, as we note an 
equal fraction of low metallicity dwarf galaxies in both the void and denser 
regions.  Due to their low gas-phase oxygen abundances, these 287 dwarf galaxies 
have some of the higher N/O ratios of the star-forming dwarf galaxies sample 
studied.  While the metallicities of these galaxies cause them to stand out in 
the relationships between metallicity and other physical quantities (stellar 
mass, color, (s)SFR), they are not unusual when studying the relationships 
between the N/O ratio and these other quantities.

% Small-scale environment
\section[Small-scale environment]{Small-scale environmental influence on dwarf galaxy evolution}
In addition to the influence of the large-scale environment on the evolution of 
dwarf galaxies, we also study the effects of the small-scale environment on dwarf 
galaxies.  We find that only the presence of a neighboring galaxy within 0.05 
\hMpc or 0.1$r_{vir}$, or the presence of a group within 0.05 \hMpc influences a 
dwarf galaxy's evolution.  Dwarf galaxies with a nearest neighbor galaxy within 
0.05 \hMpc or 0.1$r_{vir}$ tend to be bluer, have a higher sSFR, have higher 
oxygen abundances, and have lower N/O ratios than average.  This matches the 
results of \cite{Park09}, who find that higher luminosity late-late type galaxy 
pairs within 0.05$r_{vir}$ are bluer and have higher SFRs.  In contrast, dwarf 
galaxies within 0.05 \hMpc of the center of the closest group have lower oxygen 
and nitrogen abundances than average.  These results are independent of both the 
maximum relative velocity required to define a nearest neighbor, but they may 
depend on the sample (star-forming versus all dwarf galaxies).

@@

% GV galaxies
\section[GV galaxies]{Properties of green valley galaxies}
Finally, we also investigate the properties of galaxies residing in the green 
valley of the color-magnitude diagram (CMD) in an effort to understand the role 
of the environment on a galaxy's evolution through the color-magnitude diagram.  
We discover that we can define galaxies which are transitioning through the 
green valley of the CMD by combining the galaxy's color, color gradient, and 
inverse concentration index.  Galaxies with a value aimc $< 25$ for the 
morphological type as calculated in the KIAS-VAGC exist in the green valley 
portion of the UV-optical CMD.  Galaxies defined as early types (morphological 
type values equal to 1 or 2) are in the red cloud, while those with 
morphological type values greater than 25 are in the blue sequence.  With this 
quantitative definition for galaxies transitioning through the green valley, we 
can begin to understand the properties of green valley galaxies and their 
evolution.

Based on our analysis, green valley galaxies have stellar masses comparable to 
galaxies in the red cloud.  They have intermediate SFRs and low-to-intermediate 
sSFRs.  Green valley galaxies also have high gas-phase nitrogen abundances 
(N/H), resulting in high N/O ratios.  While their SFRs show that their star 
formation has been quenched, their stellar masses inform us that this is not due 
to any premature quenching mechanism.  The high nitrogen abundances in the green 
valley galaxies indicate that the galaxies are either no longer forming stars 
(since nitrogen is produced in lower mass stars than oxygen), or that the 
galaxies were able to synthesize both primary and secondary nitrogen (heavy 
elements were present during the last few star formation episodes to permit the 
CNO cycle to commence earlier).  This chemical abundance pattern of normal 
oxygen (O/H), high nitrogen (N/H), and high N/O ratio is also seen in galaxies 
classified as AGN, indicating that galaxies in the green valley may have an AGN.

The fraction of void galaxies that are found in the green valley is 
significantly smaller than the fraction of green valley galaxies found in denser 
regions.  Combined with the previous results of the large-scale environmental 
influence on the gas-phase chemical abundances, this indicates that void dwarf 
galaxies may be less evolved than dwarf galaxies in denser environments.

@@

A critical problem in galaxy formation is understanding how galaxies transition 
from the blue sequence to the red cloud in the optical color-magnitude diagram.  
Star formation is thought to be quenching in galaxies moving through the green 
valley, but the relevant baryonic processes (gas cooling, feedback, etc.) are 
very complex and heavily dependent.  The enrichment of the interstellar medium 
(ISM) and circumgalactic medium (CGM) of a galaxy involves many complicated 
processes, the interplay of which is not yet well understood.  Investigating the 
star formation history and chemical evolution of galaxies in the green valley 
should provide clues of the movement of a galaxy through the color-magnitude 
diagram.

With the advent of 2-dimensional spectroscopic data from SDSS MaNGA \citep{MaNGA,
SDSS13}, it is now possible to examine how the ISM and CGM are enriched over 
time.  MaNGA is the first large-scale survey using integral-field spectroscopy, 
which permits the study of spatially-resolved physical properties of galaxies 
across many different environments, morphologies, and stages of evolution.  In 
particular, it would be instructive to study the gradients of the gas-phase 
chemical abundances of galaxies in order to better understand their evolution 
through the CMD and also the influence of the environment in both large and 
small scales on the chemical evolution of these galaxies.

@@

A better knowledge of the chemical abundances of galaxies with an AGN is also 
crucial to understanding the evolution of galaxies.  Understanding how the 
presence of an AGN affects a galaxy's evolution is currently limited --- at the 
moment, most research is concentrated on the physics within an AGN.  Many 
simulations have been done to test different theories about the role of an AGN 
in a galaxy, and observations are now needed to test the results of these 
simulations.

@@

The work done here on the small-scale environment is only the beginning of what 
can be done.  In addition to studying the relationship between a galaxy's 
physical parameters and its distance to the nearest neighbor, it is also 
important to look at the ratio of the galaxy's parameters to its neighbor's and 
the distance to the nearest neighbor --- ``galactic conformity.''  These 
comparisons should include a morphological comparison, similar to the analysis 
done by \cite{Park09}.  We also find evidence of possible mergers when studying 
the influence of the small-scale environment.  Visual inspection of these dwarf 
galaxies is imperative to verify this conclusion.
